maze-dataset

### 2025-03-29 docs/paper/paper.tex
wip paper

\begin{figure}
\centering
\includegraphics{docs/paper/figures/TokenizerElement_structure.pdf}
\caption{Nested internal structure of \texttt{\_TokenizerElement}
objects inside a typical \texttt{MazeTokenizerModular} object.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{docs/paper/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

>>>>

\begin{figure}
    \centering
    \input{docs/paper/figures/TokenizerElement_structure.tikz}
    \caption{Nested internal structure of \texttt{\_TokenizerElement} objects inside a typical \texttt{MazeTokenizerModular} object.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{docs/benchmarks/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

\begin{figure}
\centering
\includegraphics{docs/benchmarks/figures/n_mazes-vs-gentime.pdf}
\caption{Maze size vs generation time}
\end{figure}
